Manuscript for foodborne-outbreak Project

### 2023-02-24 code/analysis_code/exploratory_analysis.qmd
work for part 2

## Save Graph
image_path <- here("results")
ggsave("time_v_hospitalization_pathogen_type.png", path = image_path)

@@

## Save Graph
ggsave("pathogen_type_etiology_v_hospitalizations.png", path = image_path)

@@

ggsave("bacterial_etiology_v_hospitalization_frequency.png", path = image_path)

@@

# Food Type and Hospitalizations
ggplot(training_data_final %>% 
         filter(`IFSAC Category` != "Multiple") %>% 
         filter(`IFSAC Category` != "Other"), 
       aes(x = `IFSAC Category`, y = Hospitalizations)) + 
  geom_col() + 
  labs(x = "Food Type", y = "Hospitalizations", title = "Hospitalizations by Food Type, Excluding 'Multiple' and 'Other'")
ggsave("Food_type_v_hospitalization.png", path = image_path)

@@

ggsave("Location_v_hospitalization.png", path = image_path)

@@

## Save Graph
ggsave("time_v_illness_pathogen_type.png", path = image_path)

@@

## Save Graph
ggsave("pathogen_type_etiology_v_illness.png", path = image_path)

@@

# Save Graph
ggsave("bacterial_etiology_v_outbreak_frequency.png", path = image_path)

@@

# Save Graph
ggsave("food_type_v_illness_frequency.png", path = image_path)

@@

# Save Graph
ggsave("Location_v_Illness.png", path = image_path)

>>>>

## Save Graph
image_path <- here("results")
ggsave("time_v_hospitalization_pathogen_type.png", path = image_path, width = 3000, height = 2000, units = "px")

@@

## Save Graph
ggsave("pathogen_type_etiology_v_hospitalizations.png", path = image_path, width = 3000, height = 2000, units = "px")

@@

ggsave("bacterial_etiology_v_hospitalization_frequency.png", path = image_path, width = 3000, height = 2000, units = "px")

@@

# Food Type and Hospitalizations
ggplot(training_data_final %>% 
         filter(`IFSAC Category` != "Multiple") %>% 
         filter(`IFSAC Category` != "Other"), 
       aes(x = `IFSAC Category`, y = Hospitalizations)) + 
  geom_col() + 
  labs(x = "Food Type", y = "Hospitalizations", title = "Hospitalizations by Food Type, Excluding 'Multiple' and 'Other'")
ggsave("Food_type_v_hospitalization.png", path = image_path, width = 3000, height = 2000, units = "px")

@@

ggsave("Location_v_hospitalization.png", path = image_path, width = 3000, height = 2000, units = "px")

@@

## Save Graph
ggsave("time_v_illness_pathogen_type.png", path = image_path, width = 3000, height = 2000, units = "px")

@@

## Save Graph
ggsave("pathogen_type_etiology_v_illness.png", path = image_path, width = 3000, height = 2000, units = "px")

@@

# Save Graph
ggsave("bacterial_etiology_v_outbreak_frequency.png", path = image_path, width = 3000, height = 2000, units = "px")

@@

# Save Graph
ggsave("food_type_v_illness_frequency.png", path = image_path, width = 3000, height = 2000, units = "px")

@@

# Save Graph
ggsave("Location_v_Illness.png", path = image_path, width = 3000, height = 2000, units = "px")

### 2023-02-24 products/manuscript/Manuscript.qmd
work for part 2

*Use a combination of text/tables/figures to explore and describe your data. Show the most important descriptive results here. Additional ones should go in the supplement. Even more can be in the R and Quarto files that are part of your project.*

@tbl-summarytable shows a summary of the data.

Note the loading of the data providing a **relative** path using the `../../` notation.
(Two dots means a folder up).
You never want to specify an **absolute** path like `C:\ahandel\myproject\results\` because if you share this with someone, it won't work for them since they don't have that path.
You can also use the `here` R package to create paths.
See examples of that below.

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable)
```

## Basic statistical analysis

*To get some further insight into your data, if reasonable you could compute simple statistics (e.g. simple models with 1 predictor) to look for associations between your outcome(s) and each individual predictor variable. Though note that unless you pre-specified the outcome and main exposure, any "p\<0.05 means statistical significance" interpretation is not valid.*

@fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by sex."
#| echo: FALSE
knitr::include_graphics(here("results","height_weight_stratified.png"))
```

## Full analysis

>>>>

### Training Data

![Figure 2: Hospitalizations by Food Type.](images/Food_type_v_hospitalization-01.png)

```{r}
rmarkdown::paged_table(readRDS("../../results/state_v_hospitalization_training.rds"))
```

### Analysis Data

![Figure 1. Year vs Illnesses Caused by Pathogen Type](images/time_v_illness_pathogen_type.png)

![Figure 3. Illnesses by outbreak location.](images/Location_v_Illness.png)

![Figure 4. Bacterial etiology by outbreak frequency.](images/bacterial_etiology_v_outbreak_frequency.png)

## Basic Statistical Analysis

## Full Analysis
